25-Figure3-051821

### 2021-08-23 notebooks/03-Fig3abde_4acd-051821.Rmd
adjusted notebooks by removing default labels that cause errors

# Load packages
```{r, message=FALSE,warning=FALSE}
#library(tidyverse)
if (!require('tidyverse')) {
   remotes::install_version("tidyverse", version = "1.3.0", repos = "http://cran.us.r-project.org")
   library(tidyverse)
}
if (!require('glue')) {
   remotes::install_version("glue", version = "1.4.1", repos = "http://cran.us.r-project.org")
   library(glue)
}
if (!require('cowplot')) {
   remotes::install_version("cowplot", version = "1.0.0", repos = "http://cran.us.r-project.org")
   library(cowplot)
}
if (!require('ggpubr')) {
   remotes::install_version('foreign',version="0.8-72", repos = "http://cran.us.r-project.org")
   remotes::install_version("ggpubr", version = "0.4.0", repos = "http://cran.us.r-project.org")
   library(ggpubr)
}
if (!require('ggsignif')) {
   remotes::install_version("ggsignif", version = "0.6.0", repos = "http://cran.us.r-project.org")
   library(ggsignif)
}
if (!require('RColorBrewer')) {
   remotes::install_version("RColorBrewer", version = "0.6.0", repos = "http://cran.us.r-project.org")
   library(RColorBrewer)
}
col <- brewer.pal(n = 9, name = "Set1")
sensor_colors <- col[2:6] # brewer.pal(n = 6, name = "Set1")
effector_colors <- col[7:9] # brewer.pal(n=3, name= "Set1_r")
if(!require("FSA")){
  remotes::install_github('droglenc/FSA')
}
```

```{r, include=FALSE, eval=FALSE}
# sessionInfo()
# smake<-setClass("smake",slots=list(input="list"))
# snakemake <- new("smake",input=list("sensor_connectivity_df"="../data/interim/sensor_connectivity_df.csv", "pcc_df"='../data/interim/pcc_df.csv',"sensors_pcc"="../data/interim/sensors_df.csv",'effector_pcc'='../data/interim/effectors_df.csv',
# "rwr_row"="../data/interim/rwr_ranked_goa_rows.csv","prs_row"="../data/interim/prs_ranked_goa_rows.csv",
# "rwr_column"="../data/interim/rwr_ranked_goa_columns.csv","prs_column"="../data/interim/prs_ranked_goa_columns.csv"))
```
# Load necessary data
```{r}

@@

## D
```{r}
sensors_pcc %>% drop_na()%>%kruskal.test(deg~go_group,data=.)

sensors_pcc$go_group <- as.factor(sensors_pcc$go_group)%>%fct_recode(
  `Iron ion transport`  = "cellular response to iron ion starvation",
  `Mitochondria-nucleus\nsignaling pathway\nand\nTricarboxylic acid cycle`="mitochondria-nucleus signaling pathway",
  `Phenylalanine transport`="phenylalanine transport",
  `Hexose metabolic process`="hexose metabolic process",
  `Tricarboxylic acid cycle`="tricarboxylic acid cycle"
)
sens_deg_comp <- ggplot(sensors_pcc %>% drop_na() %>% right_join(pcc_df)%>% mutate(go_group = factor(replace_na(as.character(go_group),"Non-sensor genes")),go_group=fct_reorder(go_group, sens),go_group=fct_relevel(go_group,'Non-sensor genes',after=Inf)), aes(x = go_group, y = deg, fill = go_group)) +
  geom_boxplot(
    outlier.shape=NA) +
  xlab("") +
  ylab("Degree") +
  scale_fill_manual(values = c(sensor_colors[1:5],'black')) +
  ggpubr::stat_compare_means(method = "kruskal.test", label.x.npc = .3) +
  theme_bw() +
  theme(
        axis.title.y=element_text(size=14),
        axis.text.y=element_text(size=10),
    axis.text.x = element_blank(), legend.title = element_blank(),
    legend.text = element_text(margin = margin(t = 10, b = 10))
  )+scale_y_log10()
sens_deg_comp

@@

sensors_sens_pval <- FSA::dunnTest(sens ~ go_group, sensors_pcc)
sensors_sens_pval$res[sensors_sens_pval$res$P.adj < 0.1, ]

sens_sens_comp <- ggplot(sensors_pcc %>% drop_na() %>% mutate(go_group = fct_reorder(go_group, sens)) %>%
  mutate(sens_norm = sens / 5183), aes(x = go_group, y = sens_norm, fill = go_group)) +
  geom_boxplot() +
  geom_signif(
    comparisons = list(
      c("Hexose metabolic process", "Phenylalanine transport"), c("Tricarboxylic acid cycle", "Phenylalanine transport")#,
      #c("phenylalanine\ntransport", "protein folding")
    ),
    annotation = c("**", "**"), y_position = c(0.007, 0.0075)#, 0.008)
  ) +
  xlab("") +
  ylab("Sensitivity") +
  scale_fill_manual(values = sensor_colors) +
  theme_bw() +
  theme(
        axis.title.y=element_text(size=14),
        axis.text.y=element_text(size=10),
        axis.text.x = element_blank(),
        legend.title = element_blank())+
        ylim(NA, 0.008)

sens_sens_comp
```

@@

## C
```{r}
# effector_pcc$go_group <- as.factor(effector_pcc$go_group)%>%fct_recode(
#   golgi = "phosphatidylinositol biosynthetic process",
#   mito = "mitochondrial cytochrome c oxidase assembly",
#   chromosome = "replication fork protection"
# )
effector_pcc  <- effector_pcc%>%mutate(go_group=fct_reorder(go_group, eff), 
          go_group = factor(go_group,labels=c('chromosome','golgi','mito')))
res.aov <- kruskal.test(deg~go_group, data= effector_pcc)
res.aov
effector_eff_pval <- FSA::dunnTest(eff ~ go_group, effector_pcc)
effector_eff_pval$res[effector_eff_pval$res$P.adj < 0.1, ]
effector_deg_pval <- FSA::dunnTest(deg ~ go_group, effector_pcc)
effector_deg_pval$res[effector_deg_pval$res$P.adj < 0.1, ]

effector_pcc %>% right_join(pcc_df)%>% mutate(go_group = factor(replace_na(as.character(go_group),"Others")),go_group=fct_relevel(go_group,'Others',after=Inf))%>%
  kruskal.test(deg~go_group, data=.)

eff_deg_comp <- ggplot(effector_pcc %>% right_join(pcc_df)%>% mutate(go_group = factor(replace_na(as.character(go_group),"Others")),go_group=fct_relevel(go_group,'Others',after=Inf)), 
                       aes(x = go_group, y = deg, fill = go_group)) +
  geom_boxplot(outlier.shape = NA) +
  scale_fill_manual(
    values = c(effector_colors,'black'),
    labels = c("Chromosome\nSegregation", "Golgi vesicle\nTransport", "Respiratory complex\nassembly",'Non-effector genes')
  ) +
  xlab("") +
  ylab("Degree") +
  theme_bw() +
  geom_signif(
    comparisons = list(c("golgi", "chromosome"), c("golgi", "mito"), c("mito", "chromosome")),
    annotation = c("**", "***", "ns"),
    y_position = c(115, 120, 130)
  ) +
  theme(
       axis.text.y=element_text(size=10),
        axis.title.y=element_text(size=14),legend.title = element_blank(),  axis.text.x = element_blank(), legend.text = element_text(margin = margin(t = 10, b = 10))) # , legend.spacing.y = unit(2,'in'))+
eff_deg_comp
```

@@

eff_eff_comp <- ggplot(effector_pcc %>% mutate(go_group = fct_reorder(go_group, eff)) %>%
  mutate(eff_norm = eff / 5183), aes(x = go_group, y = eff_norm, fill = go_group)) +
  geom_boxplot() +
  xlab("") +
  ggpubr::stat_compare_means(method = "kruskal.test") +
  scale_fill_manual(values = effector_colors,
  labels = c("Chromosome\nSegregation", "Golgi vesicle\nTransport", "Respiratory complex\nassembly")) +
  ylab("Effectiveness") +
  theme_bw() +
  theme(
        axis.text.y=element_text(size=10),
        axis.title.y=element_text(size=14),axis.text.x = element_blank(), legend.title = element_blank())
eff_eff_comp
```

>>>>

# Load packages
```{r message=FALSE, warning=FALSE}
#library(tidyverse)
if (!require('tidyverse')) {
   remotes::install_version("tidyverse", version = "1.3.0", repos = "http://cran.us.r-project.org")
   library(tidyverse)
}
if (!require('glue')) {
   remotes::install_version("glue", version = "1.4.1", repos = "http://cran.us.r-project.org")
   library(glue)
}
if (!require('cowplot')) {
   remotes::install_version("cowplot", version = "1.0.0", repos = "http://cran.us.r-project.org")
   library(cowplot)
}
if (!require('ggpubr')) {
   remotes::install_version('foreign',version="0.8-72", repos = "http://cran.us.r-project.org")
   remotes::install_version("ggpubr", version = "0.4.0", repos = "http://cran.us.r-project.org")
   library(ggpubr)
}
if (!require('ggsignif')) {
   remotes::install_version("ggsignif", version = "0.6.0", repos = "http://cran.us.r-project.org")
   library(ggsignif)
}
if (!require('RColorBrewer')) {
   remotes::install_version("RColorBrewer", version = "0.6.0", repos = "http://cran.us.r-project.org")
   library(RColorBrewer)
}
col <- brewer.pal(n = 9, name = "Set1")
sensor_colors <- col[2:6] # brewer.pal(n = 6, name = "Set1")
effector_colors <- col[7:9] # brewer.pal(n=3, name= "Set1_r")
if(!require("FSA")){
  remotes::install_github('droglenc/FSA')
}
```

```{r include=FALSE, eval=FALSE}
# sessionInfo()
# smake<-setClass("smake",slots=list(input="list"))
# snakemake <- new("smake",input=list("sensor_connectivity_df"="../data/interim/sensor_connectivity_df.csv", "pcc_df"='../data/interim/pcc_df.csv',"sensors_pcc"="../data/interim/sensors_df.csv",'effector_pcc'='../data/interim/effectors_df.csv',
# "rwr_row"="../data/interim/rwr_ranked_goa_rows.csv","prs_row"="../data/interim/prs_ranked_goa_rows.csv",
# "rwr_column"="../data/interim/rwr_ranked_goa_columns.csv","prs_column"="../data/interim/prs_ranked_goa_columns.csv"))
```
# Load necessary data
```{r}

@@

## D
```{r}
#sensors_pcc %>% drop_na()%>%kruskal.test(deg~go_group,data=.)

sensors_pcc$go_group <- as.factor(sensors_pcc$go_group)
sens_deg_comp <- ggplot(sensors_pcc %>% drop_na() %>% right_join(pcc_df)%>% mutate(go_group = factor(replace_na(as.character(go_group),"Non-sensor genes")),go_group=fct_reorder(go_group, sens),go_group=fct_relevel(go_group,'Non-sensor genes',after=Inf)), aes(x = go_group, y = deg, fill = go_group)) +
  geom_boxplot(
    outlier.shape=NA) +
  xlab("") +
  ylab("Degree") +
  scale_fill_manual(values = c(sensor_colors[1:5],'black')) +
  #ggpubr::stat_compare_means(method = "kruskal.test", label.x.npc = .3) +
  theme_bw() +
  theme(
        axis.title.y=element_text(size=14),
        axis.text.y=element_text(size=10),
    axis.text.x = element_blank(), legend.title = element_blank(),
    legend.text = element_text(margin = margin(t = 10, b = 10))
  )+scale_y_log10()
sens_deg_comp

@@

if(nrow(sensors_pcc%>%drop_na(go_group))!=0){
sens_sens_comp <- ggplot(sensors_pcc %>% drop_na() %>% #mutate(go_group = fct_reorder(go_group, sens)) %>%
  mutate(sens_norm = sens / 5183), aes(x = go_group, y = sens_norm, fill = go_group)) +
  geom_boxplot() +
#   geom_signif(
#     comparisons = list(
#       c("Hexose metabolic process", "Phenylalanine transport"), c("Tricarboxylic acid cycle", "Phenylalanine transport")#,
#       #c("phenylalanine\ntransport", "protein folding")
#     ),
#     annotation = c("*", "*"), y_position = c(0.007, 0.0075)#, 0.008)
#   ) +
  xlab("") +
  ylab("Sensitivity (a.u.)") +
  scale_fill_manual(values = sensor_colors) +
  theme_bw() +
  theme(
        axis.title.y=element_text(size=14),
        axis.text.y=element_text(size=10),
        axis.text.x = element_blank(),
        legend.title = element_blank())+
        ylim(NA, 0.008)

sens_sens_comp}
```

@@

## C
```{r}
# effector_pcc$go_group <- as.factor(effector_pcc$go_group)%>%fct_recode(
#   golgi = "phosphatidylinositol biosynthetic process",
#   mito = "mitochondrial cytochrome c oxidase assembly",
#   chromosome = "replication fork protection"
# )
effector_pcc  <- effector_pcc#%>%mutate(go_group=fct_reorder(go_group, eff))
# res.aov <- kruskal.test(deg~go_group, data= effector_pcc)
# res.aov
effector_eff_pval <- FSA::dunnTest(eff ~ go_group, effector_pcc)
effector_eff_pval$res[effector_eff_pval$res$P.adj < 0.1, ]
effector_deg_pval <- FSA::dunnTest(deg ~ go_group, effector_pcc)
effector_deg_pval$res[effector_deg_pval$res$P.adj < 0.1, ]

effector_pcc %>% right_join(pcc_df)

eff_deg_comp <- ggplot(effector_pcc %>% right_join(pcc_df)%>% mutate(go_group = factor(replace_na(as.character(go_group),"Others")),go_group=fct_relevel(go_group,'Others',after=Inf)), 
                       aes(x = go_group, y = deg, fill = go_group)) +
  geom_boxplot(outlier.shape = NA) +
#   scale_fill_manual(
#     values = c(effector_colors,'black'),
#     labels = c("Chromosome\nSegregation", "Golgi vesicle\nTransport", "Respiratory complex\nassembly",'Non-effector genes')
#   ) +
  xlab("") +
  ylab("Degree") +
  theme_bw() +
#   geom_signif(
#     comparisons = list(c("golgi", "chromosome"), c("golgi", "mito"), c("mito", "chromosome")),
#     annotation = c("*", "***", "ns"),
#     y_position = c(115, 120, 130)
#   ) +
  theme(
       axis.text.y=element_text(size=10),
        axis.title.y=element_text(size=14),legend.title = element_blank(),  axis.text.x = element_blank(), legend.text = element_text(margin = margin(t = 10, b = 10))) # , legend.spacing.y = unit(2,'in'))+
eff_deg_comp
```

@@

eff_eff_comp <- ggplot(effector_pcc %>% #mutate(go_group = fct_reorder(go_group, eff)) %>%
  mutate(eff_norm = eff / 5183), aes(x = go_group, y = eff_norm, fill = go_group)) +
  geom_boxplot() +
  xlab("") +
  #ggpubr::stat_compare_means(method = "kruskal.test") +
#   scale_fill_manual(values = effector_colors,
#   labels = c("Chromosome\nSegregation", "Golgi vesicle\nTransport", "Respiratory complex\nassembly")) +
  ylab("Effectiveness (a.u.)") +
  theme_bw() +
  theme(
        axis.text.y=element_text(size=10),
        axis.title.y=element_text(size=14),axis.text.x = element_blank(), legend.title = element_blank())
eff_eff_comp
```
